### 2014-06-13 kypchak-morphfest-2014/poster.tex
better logos, more content
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@54176 72bbbca6-d526-0410-a7d9-f06f51895060

	\begin{poster}{
			grid=false,
			%eyecatcher=false,
			borderColor=bordercol,
			headerColorOne=headercolone,
			headerColorTwo=headercoltwo,
			headerFontColor=white,
			% Only simple background color used, no shading, so boxColorTwo isn't necessary
			boxColorOne=boxcolor,
			headershape=roundedright,
  headerborder=open,
  headerheight=0.1\textheight,
  %headershape=roundedright,
  %headershade=plain,
  %headerfont=\Large\textsf, %Sans Serif
			%headerfont=\Large\sf\bf,
			textborder=rectangle,
			%background=plain,
			%background=user,
			background=none,
			headerborder=open,
			boxshade=plain,
			textborder=roundedleft,
			columns=6,
		}{
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 242 203]{apertium}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 612 792]{apertium2}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 203 242]{apertium3}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 242 203]{apertium3a}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 242 203]{apertium4}
			%\hspace{-2em}
			\includegraphics[angle=90,height=8em]{apertium5a}%\hspace{-2em}
			%Eye Catcher, empty if option eyecatcher=false - unused
			%\begin{minipage}[t]{0.2\textwidth}
				\hspace{1cm}\includegraphics[height=6.5em]{iu_tab}
				\hspace{1cm}\includegraphics[height=6.5em]{kfu}
				\hspace{1cm}\includegraphics[height=6.5em]{uitlogo}
			%\end{minipage}
		}{
			{\vspace{0pt}\hspace{1cm}
			{\titlefont \textsc{Designing finite-state morphological transducers\\for Kypchak languages}}}
		}{
			%Jonathan North Washington {\small (Indiana University, \texttt{jonwashi@indiana.edu})}, Mirlan Ipasov {\small (International Ataturk Alatoo University, \texttt{mipasov@gmail.com})}, Francis M.\ Tyers {\small (Universitat d'Alacant, \texttt{ftyers@dlsi.ua.es})}

@@

	\headerbox{Kypchak languages}{name=kypchaklgs,column=0,row=0}{
		\vspace{0.5ex}
		\includegraphics[width=\textwidth]{map}
		\vspace{-1.1em}  % -1.25em
		\begin{itemize}
			\item Turkic languages (SOV, agglutinative, vowel harmony)
		\end{itemize}

	\scalebox{0.85}{
		\begin{tabular}{lllll}
			\toprule
				 & \textbf{Kyrgyz} & \textbf{Kazakh} & \textbf{Tatar} & \textbf{Kumyk} \\
				 & /{\qipa qɯɾʁɯz}/ & /{\qipa qɑzɑq}/ & /{\qipa tɒtɑɾ}/ & /{\qipa qumuq}/ \\
				classification & Eastern & Southern & Northern & Western \\
			\midrule
				\multicolumn{4}{l}{population of speakers} \\
			\midrule
				number & 3M & 8M-12M & 5.4M & 430K \\
				primary & Kyrgyzstan & Kazakhstan & Tatarstan & Dagestan \\
				secondary & China, etc. & China, Mongolia & Bashqortostan & --- \\
			\midrule
				\multicolumn{4}{l}{external influences} \\
			\midrule
				Mongolic & moderate & moderate & light & light \\
				Oghuz & — & — & light & moderate \\
				Persian & heavy & heavy & heavy & heavy \\
				Russian & heavy & heavy & heavy & heavy \\
			\bottomrule
		\end{tabular}
	}
%			\begin{itemize}
%				\item Similar historically to Southern Altay
%				\item Similar by convergence to Kazakh, Uzbek
%			\end{itemize}
%			\item Spoken in
%			\begin{itemize}
%				\item Kyrgyzstan, as co-official language\\
%				\textit{high levels of bilingualism with Russian}
%				\item China, Tajikistan, Uzbekistan
%			\end{itemize}
%			\item Over 3 million native speakers\\(estimate based on data from Ethnologue) %\citep{lewis2009}
%			\item Our transducer based on written Kyrgyz of the former Soviet Union (literary and colloquial standards)
%		\end{itemize}
	}

@@

		\htwo{Transducers for Turkic languages}
		\begin{itemize}
			\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			\item Kyrgyz (\hiliteone{Washington et al., 2012})%\\
			\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			\item our Kazakh, Tatar, Kumyk: all \hiliteone{GPL (=free and open)}!
		\end{itemize}

@@

		\pex[aboveexskip=0pt,belowexskip=3pt,aboveglftskip=0pt]\label{ex:sent}
			\begingl
				\gla[everygla={\qipa }] Кудай Өзү жаратканынын баарына карап, {} өтө жакшы экенин көрдү. //
				\glb[everyglb={\qipa }] Құдай Өзінің жаратқандарының бәріне қарап, {} өте жақсы екенін көрді. //
				\glb[everyglb={\qipa }] Аллаһ Үзе яраткан нәрсәләргә карап, аларның бик яхшы икәнен күрде. //
				\glb[everyglb={\qipa }] Аллагь Оьзю яратгъан затлагъа къарап, олар бек яхшы экенин гёрген. //
				\glb God own-his created [everything/thing-s]-to looked.at, they/their very good being saw. // 
				\glft \eng{God looked at everything he had created and saw that it was very good. (Bible, Genesis 1:31)} //
			\endgl
		\xe

		\htwo{Output}
\scalebox{0.81}{
\begin{tabular}{llll}
\toprule
 \textbf{Kyrgyz} (\textbf{kir}) & \textbf{Kazakh} (\textbf{kaz}) & \textbf{Tatar} (\textbf{tat}) & \textbf{Kumyk} (\textbf{kum}) \\
\midrule
\texttt{Кудай Өзү жаратканынын баарына} & \texttt{Құдай Өзінің жаратқандарының бәріне} & \texttt{Аллаһ Үзе яраткан нәрсәләргә карап,} & \texttt{Аллагь Оьзю яратгъан затлагъа} \\
\texttt{карап, өтө жакшы экенин көрдү.} & \texttt{қарап, өте жақсы екенін көрді.} & \texttt{аларның бик яхшы икәнен күрде.} & \texttt{къарап, олар бек яхшы экенин гёрген.} \\
\midrule
	\texttt{Кудай\tag{n}\tag{nom}} & \texttt{Құдай\tag{n}\tag{nom}} & \texttt{Аллаһ\tag{n}\tag{nom}} & \texttt{Аллагь\tag{n}\tag{nom}} \\
	\texttt{Өз\tag{prn}\tag{ref}\tag{px3sp}\tag{nom}} & \texttt{Өз\tag{prn}\tag{ref}\tag{px3sp}\tag{gen}} & \texttt{Үз\tag{prn}\tag{ref}\tag{px3sp}\tag{nom}} & \texttt{Оьз\tag{prn}\tag{ref}\tag{px3sp}\tag{nom}} \\
	\texttt{жарат\tag{v}\tag{tv}\tag{ger\_past}\tag{px3sp}\tag{gen}} & \texttt{жарат\tag{v}\tag{tv}\tag{ger\_past}\tag{pl}\tag{px3sp}\tag{gen}} & \texttt{ярат\tag{v}\tag{tv}\tag{gpr\_past}} & \texttt{ярат\tag{v}\tag{tv}\tag{gpr\_past}} \\
	\texttt{баары\tag{prn}\tag{qnt}\tag{px3sp}\tag{dat}} & \texttt{бәрі\tag{prn}\tag{qnt}\tag{px3sp}\tag{dat}} & \texttt{нәрсә\tag{n}\tag{pl}\tag{dat}} & \texttt{зат\tag{n}\tag{pl}\tag{dat}} \\
	\texttt{кара\tag{v}\tag{tv}\tag{gna\_perf}} & \texttt{қара\tag{v}\tag{tv}\tag{gna\_perf}} & \texttt{кара\tag{v}\tag{tv}\tag{gna\_perf}} & \texttt{къара\tag{v}\tag{tv}\tag{gna\_perf}} \\ 
	\texttt{,\tag{cm}} & \texttt{,\tag{cm}} & \texttt{,\tag{cm}} & \texttt{,\tag{cm}} \\
	 --- & ---      & \texttt{алар\tag{prn}\tag{pers}\tag{p3}\tag{pl}\tag{gen}} & \texttt{олар\tag{prn}\tag{pers}\tag{p3}\tag{pl}\tag{nom}} \\
	\texttt{өтө\tag{adv}} & \texttt{өте\tag{adv}} & \texttt{бик\tag{adv}} & \texttt{бек\tag{adv}} \\
	\texttt{жакшы\tag{adj}} & \texttt{жақсы\tag{adj}} & \texttt{яхшы\tag{adj}} & \texttt{яхшы\tag{adj}} \\
	\texttt{э\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} & \texttt{е\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} & \texttt{и\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} & \texttt{э\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} \\
	\texttt{көр\tag{v}\tag{tv}\tag{ifi}\tag{p3}\tag{sg}} & \texttt{көр\tag{v}\tag{tv}\tag{ifi}\tag{p3}\tag{sg}} & \texttt{күр\tag{v}\tag{tv}\tag{past}\tag{p3}\tag{sg}} & \texttt{гёр\tag{v}\tag{tv}\tag{past}\tag{p3}\tag{sg}} \\  
	\texttt{.\tag{sent}} & \texttt{.\tag{sent}} & \texttt{.\tag{sent}} & \texttt{.\tag{sent}} \\
\bottomrule
\end{tabular}
}

@@

\vspace{-1.5em}
\setlength{\columnsep}{-1em}
\setlength{\topsep}{-\parskip}
%\spacing{0.8}
\begin{multicols}{4}
\begin{tabbing}
  \texttt{{\small \tag{n}}}\hspace{1.5em} \=  Noun\\[-0.5ex]
%  \texttt{{\small <np>}} \> Proper noun\\[-0.5ex]
  \texttt{{\small \tag{v}}} \>  Verb\\[-0.5ex]
  \texttt{{\small \tag{prn}}} \> Pronoun \\[-0.5ex]
  \texttt{{\small \tag{det}}} \>  Determiner\\[-0.5ex]
%  \texttt{{\small <cnjcoo>}} \> Coord. conjunct.\\[-0.5ex]
%  \texttt{{\small <cnjadv>}} \> Adv. conjunct.\\[-0.5ex]
  \texttt{{\small \tag{adj}}} \> Adjective\\[-0.5ex]
  \texttt{{\small \tag{adv}}} \> Adverb\\[-0.5ex]
%  \texttt{{\small <vaux>}} \> Auxiliary verb\\[-0.5ex]
%  \texttt{{\small <cop>}} \> Copula\\[-0.5ex]
  \texttt{{\small \tag{iv}}} \> Intransitive\\[-0.5ex]
  \texttt{{\small \tag{tv}}} \> Transitive\\[-0.5ex]
%  \texttt{{\small <p2>}} \> Second person\\[-0.5ex]
  \texttt{{\small \tag{p3}}} \> Third person\\[-0.5ex]
%  \texttt{{\small <ant>}} \> Anthroponym\\[-0.5ex]
%  \texttt{{\small <dem>}} \> Demonstrative\\[-0.5ex]
%  \texttt{{\small <m>}} \> Masculine\\[-0.5ex]
%  \texttt{{\small <sg>}} \> Singular\\[-0.5ex]
  \texttt{{\small \tag{pl}}} \> Plural\\[-0.5ex]
  \texttt{{\small \tag{nom}}} \> `Nominative'\\[-0.5ex]
  \texttt{{\small \tag{gen}}} \> Genitive\\[-0.5ex]
  \texttt{{\small \tag{acc}}} \> Accusative\\[-0.5ex]
  \texttt{{\small \tag{dat}}} \> Dative\\[-0.5ex]
  \texttt{{\small \tag{qnt}}} \> Quantifier \\[-0.5ex]
%  \texttt{{\small \tag{itg}}} \> Interrogative \\[-0.5ex]
  \texttt{{\small \tag{ref}}} \> Reflexive \\[-0.5ex]
  \texttt{{\small \tag{pers}}} \> Personal \\[-0.5ex]
%  \texttt{{\small <loc>}} \> Locative\\[-0.5ex]
%  \texttt{{\small <px3sg>}} \> 3rd person poss. (Singular)\\[-0.5ex]
  \texttt{{\small \tag{cm}}} \> Comma\\[-0.5ex]
  \texttt{{\small \tag{sent}}} \> Sentence\\[-0.5ex]
%  \texttt{{\small <px3pl>}} \> 3rd person poss. (Plural)\\[-0.5ex]
%  \texttt{{\small <neg>}} \> Negative\\[-0.5ex]
%  \texttt{{\small <aor>}} \> Aorist\\[-0.5ex]
  \texttt{{\small \tag{past}}} \> Past (General) \\[-0.5ex]
  \texttt{{\small \tag{ifi}}} \> Past \\[-0.5ex]
  	\> \hspace{0.5em}(Eyewitness/Recent) \\[-0.5ex]
  \\[-0.5ex]
  \\[-0.5ex]
  \texttt{{\small \tag{px3sp}}} \hspace{1.1em} \= 3rd person poss.\\[-0.5ex]
  	\> \hspace{0.5em}(Singular/Plural)\\[-0.5ex]
%  \texttt{{\small <imp>}} \> Imperative\\[-0.5ex]
  \texttt{{\small \tag{gna\_perf}}} \> Verbal adverb \\[-0.5ex]
  	\> \hspace{0.5em}(Perfect)\\[-0.5ex]
  \texttt{{\small \tag{gpr\_past}}} \> Verbal adjective \\[-0.5ex]
  	\> \hspace{0.5em}(Past)\\[-0.5ex]
  \texttt{{\small \tag{ger\_past}}} \> Verbal noun (Past)
%  \texttt{{\small <prc\_impf>}} \> Participle (Imperfect)\\[-0.5ex]
%  \texttt{{\small <prc\_irre>}} \> Participle (Irrealis)\\[-0.5ex]
%  \texttt{{\small <prc\_real>}} \> Participle (Realis)\\[-0.5ex]

@@

		\headerbox{Categorisation}{name=lexc,below=exout,column=1}{
		%\headerbox{Morphophonology}{name=morphophon,below=morphtrans}{
			\begin{itemize}
				\item Other Turkic transducers:\ \texttt{0}-derivation (\hilitetwo{overgenerates})
				\item Our approach:\ categorisation (e.g., adjectives, below)
			\end{itemize}

@@

%		\scalebox{0.8}{
%			\begin{tabular}{lll}
%				\toprule
%				\textbf{type} & \textbf{lang} & \textbf{contents} \\ % & \textbf{origin} \\
%				\midrule
%				Encyclopædic & kaz & Wikipedia \\ % wpdump & 20131006 \\
%					& tat & Wikipedia \\ % wpdump & 20130225 \\
%					& kum & — \\ % — & — \\
%				\midrule
%				News & kaz & RFE/RL (azattyq.org) \\ % RFE/RL & azattyq.org 2010 \\
%					& tat & tat.tatar-inform.ru \\ % Татар-информ & tat.tatar-inform.ru 2005-2011 \\
%					& kum & Ёлдаш (yoldash.etnosmi.ru) \\ % Ёлдаш & yoldash.etnosmi.ru \\
%				\midrule
%				Religion & kaz & Quran + Bible \\ % quran + bible & kkitap.net, kuran.kz \\
%					& tat & Quran + New Testament \\ % quran + nt & ibt.org.ru, tanzil.net \\
%					& kum & Genesis + New Testament \\ % genesis + nt & ibt.org.ru \\
%				\bottomrule
%			\end{tabular}
%		}
		\scalebox{0.78}{
			\begin{tabular}{llll}
				\toprule
					& \textbf{Wikipedia} & \textbf{News} & \textbf{Religion} \\
				\midrule
					\texttt{\textbf{kaz}} & Wikipedia & azattyk.org & Quran + Bible \\
					\texttt{\textbf{tat}} & Wikipedia & tat.tatar-inform.ru & Quran + New Testament \\
					\texttt{\textbf{kum}} & --- & yoldash.etnosmi.ru & Genesis + New Testament \\
				\bottomrule
			\end{tabular}

@@

					\multirow{3}{*}{\texttt{\textbf{tat}}} & \multirow{3}{*}{{\qipa е}} & {\qipa э / C \_} & {\qipa дәр\hiliteone{е}сл\hilitetwo{ә}р} \eng{lessons} \\
						&	& {\qipa /j/+ы} & {\qipa \hiliteone{е}лл\hilitetwo{а}р} \eng{years} \\
						&	& {\qipa /j/+э} & {\qipa ег\hiliteone{е}тл\hilitetwo{ә}р} \eng{boys} \\
				\midrule

@@

				\item Turkic RBMT mailing list (>25 subscribers):\\
				\texttt{apertium-turkic@lists.sourceforge.net}\\
				\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item See our paper in the LREC 2014 proceedings
				\item And feel free to contact the authors any time!
			\end{itemize}
			%\vspace{2.8ex}
		}

>>>>

	\begin{poster}{
			grid=false,
			%eyecatcher=false,
			borderColor=bordercol,
			headerColorOne=headercolone,
			headerColorTwo=headercoltwo,
			headerFontColor=white,
			% Only simple background color used, no shading, so boxColorTwo isn't necessary
			boxColorOne=boxcolor,
			headershape=roundedright,
  headerborder=open,
  headerheight=0.1\textheight,
  %headershape=roundedright,
  %headershade=plain,
  %headerfont=\Large\textsf, %Sans Serif
			%headerfont=\Large\sf\bf,
			textborder=rectangle,
			%background=plain,
			%background=user,
			background=none,
			headerborder=open,
			boxshade=plain,
			textborder=roundedleft,
			columns=6,
		}{
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 242 203]{apertium}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 612 792]{apertium2}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 203 242]{apertium3}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 242 203]{apertium3a}
			%\hspace{-2em}\includegraphics[height=6.5em,bb=0 0 242 203]{apertium4}
			%\hspace{-2em}
			\includegraphics[angle=90,height=6.5em]{apertium5b}%\hspace{-2em}
			%Eye Catcher, empty if option eyecatcher=false - unused
			%\begin{minipage}[t]{0.2\textwidth}
				\hspace{1cm}\includegraphics[height=6.5em]{iu_tab}
				\hspace{1cm}\includegraphics[height=6.5em]{kfu}
				\hspace{1cm}\includegraphics[height=6.5em]{uitlogo}
			%\end{minipage}
		}{
			{\vspace{0pt}\hspace{1cm}
			{\titlefont \textsc{Designing finite-state morphological transducers\\for Kypchak languages}}}
		}{
			%Jonathan North Washington {\small (Indiana University, \texttt{jonwashi@indiana.edu})}, Mirlan Ipasov {\small (International Ataturk Alatoo University, \texttt{mipasov@gmail.com})}, Francis M.\ Tyers {\small (Universitat d'Alacant, \texttt{ftyers@dlsi.ua.es})}

@@

	\headerbox{Kypchak languages}{name=kypchaklgs,column=0,row=0}{
		\vspace{0.5ex}
		\includegraphics[width=\textwidth]{map/map}
		\vspace{-1.1em}  % -1.25em
		\begin{itemize}
			\item Turkic languages (SOV, agglutinative, vowel harmony)
		\end{itemize}

	\scalebox{0.79}{
		\begin{tabular}{lllll}
			\toprule
				 & \textbf{Kyrgyz} & \textbf{Kazakh} & \textbf{Tatar} & \textbf{Kumyk} \\
				 & /{\qipa qɯɾʁɯz}/ & /{\qipa qɑzɑq}/ & /{\qipa tɒtɑɾ}/ & /{\qipa qumuq}/ \\
				classification & Eastern & Southern & Northern & Western \\
			\midrule
				\multicolumn{4}{l}{population of speakers} \\
			\midrule
				number & 3M & 8M-12M & 5.4M & 430K \\
				primary & Kyrgyzstan & Kazakhstan & Tatarstan & Dagestan \\
				secondary & China, etc. & China, Mongolia & Bashqortostan & --- \\
			\midrule
				\multicolumn{4}{l}{external influences} \\
			\midrule
				Mongolic & moderate & moderate & light & light \\
				Oghuz & — & — & light & moderate \\
				Persian & heavy & heavy & heavy & heavy \\
				Russian & heavy & heavy & heavy & heavy \\
			\bottomrule
		\end{tabular}
	}
%			\begin{itemize}
%				\item Similar historically to Southern Altay
%				\item Similar by convergence to Kazakh, Uzbek
%			\end{itemize}
%			\item Spoken in
%			\begin{itemize}
%				\item Kyrgyzstan, as co-official language\\
%				\textit{high levels of bilingualism with Russian}
%				\item China, Tajikistan, Uzbekistan
%			\end{itemize}
%			\item Over 3 million native speakers\\(estimate based on data from Ethnologue) %\citep{lewis2009}
%			\item Our transducer based on written Kyrgyz of the former Soviet Union (literary and colloquial standards)
%		\end{itemize}
	}

@@

		\htwo{Transducers for Turkic languages}
		\begin{itemize}
			\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
		\end{itemize}

@@

		\pex[aboveexskip=0pt,belowexskip=3pt,aboveglftskip=0pt]\label{ex:sent}
			\begingl
				\gla[everygla={\qipa }] Кудай Өзү жаратканынын баарына карап, {} өтө жакшы экенин көрдү. //
				\glb[everyglb={\qipa }] Құдай Өзінің жаратқандарының бәріне қарап, {} өте жақсы екенін көрді. //
				\glb[everyglb={\qipa }] Аллаһ Үзе яраткан нәрсәләргә карап, аларның бик яхшы икәнен күрде. //
				\glb[everyglb={\qipa }] Аллагь Оьзю яратгъан затлагъа къарап, олар бек яхшы экенин гёрген. //
				\glb God own-his created [everything/thing-s]-to looked.at, they/their very good being saw. // 
				\glft \eng{God looked at everything he had created and saw that it was very good.} (Bible, Genesis 1:31) //
			\endgl
		\xe

		\htwo{Output}
\scalebox{0.68}{
\begin{tabular}{llll}
\toprule
 \textbf{Kyrgyz} (\textbf{kir}) & \textbf{Kazakh} (\textbf{kaz}) & \textbf{Tatar} (\textbf{tat}) & \textbf{Kumyk} (\textbf{kum}) \\
\midrule
\texttt{Кудай Өзү жаратканынын баарына} & \texttt{Құдай Өзінің жаратқандарының бәріне} & \texttt{Аллаһ Үзе яраткан нәрсәләргә карап,} & \texttt{Аллагь Оьзю яратгъан затлагъа} \\
\texttt{карап, өтө жакшы экенин көрдү.} & \texttt{қарап, өте жақсы екенін көрді.} & \texttt{аларның бик яхшы икәнен күрде.} & \texttt{къарап, олар бек яхшы экенин гёрген.} \\
\midrule
	\texttt{Кудай\tag{n}\tag{nom}} & \texttt{Құдай\tag{n}\tag{nom}} & \texttt{Аллаһ\tag{n}\tag{nom}} & \texttt{Аллагь\tag{n}\tag{nom}} \\
	\texttt{Өз\tag{prn}\tag{ref}\tag{px3sp}\tag{nom}} & \texttt{Өз\tag{prn}\tag{ref}\tag{px3sp}\tag{gen}} & \texttt{Үз\tag{prn}\tag{ref}\tag{px3sp}\tag{nom}} & \texttt{Оьз\tag{prn}\tag{ref}\tag{px3sp}\tag{nom}} \\
	\texttt{жарат\tag{v}\tag{tv}\tag{ger\_past}\tag{px3sp}\tag{gen}} & \texttt{жарат\tag{v}\tag{tv}\tag{ger\_past}\tag{pl}\tag{px3sp}\tag{gen}} & \texttt{ярат\tag{v}\tag{tv}\tag{gpr\_past}} & \texttt{ярат\tag{v}\tag{tv}\tag{gpr\_past}} \\
	\texttt{баары\tag{prn}\tag{qnt}\tag{px3sp}\tag{dat}} & \texttt{бәрі\tag{prn}\tag{qnt}\tag{px3sp}\tag{dat}} & \texttt{нәрсә\tag{n}\tag{pl}\tag{dat}} & \texttt{зат\tag{n}\tag{pl}\tag{dat}} \\
	\texttt{кара\tag{v}\tag{tv}\tag{gna\_perf}} & \texttt{қара\tag{v}\tag{tv}\tag{gna\_perf}} & \texttt{кара\tag{v}\tag{tv}\tag{gna\_perf}} & \texttt{къара\tag{v}\tag{tv}\tag{gna\_perf}} \\ 
	\texttt{,\tag{cm}} & \texttt{,\tag{cm}} & \texttt{,\tag{cm}} & \texttt{,\tag{cm}} \\
	 --- & ---      & \texttt{алар\tag{prn}\tag{pers}\tag{p3}\tag{pl}\tag{gen}} & \texttt{олар\tag{prn}\tag{pers}\tag{p3}\tag{pl}\tag{nom}} \\
	\texttt{өтө\tag{adv}} & \texttt{өте\tag{adv}} & \texttt{бик\tag{adv}} & \texttt{бек\tag{adv}} \\
	\texttt{жакшы\tag{adj}} & \texttt{жақсы\tag{adj}} & \texttt{яхшы\tag{adj}} & \texttt{яхшы\tag{adj}} \\
	\texttt{э\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} & \texttt{е\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} & \texttt{и\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} & \texttt{э\tag{cop}\tag{ger\_past}\tag{px3sp}\tag{acc}} \\
	\texttt{көр\tag{v}\tag{tv}\tag{ifi}\tag{p3}\tag{sg}} & \texttt{көр\tag{v}\tag{tv}\tag{ifi}\tag{p3}\tag{sg}} & \texttt{күр\tag{v}\tag{tv}\tag{past}\tag{p3}\tag{sg}} & \texttt{гёр\tag{v}\tag{tv}\tag{past}\tag{p3}\tag{sg}} \\  
	\texttt{.\tag{sent}} & \texttt{.\tag{sent}} & \texttt{.\tag{sent}} & \texttt{.\tag{sent}} \\
\bottomrule
\end{tabular}
}

@@

\vspace{-1.5em}
\setlength{\columnsep}{-1em}
\setlength{\topsep}{-\parskip}
%\spacing{0.8}
\begin{multicols}{5}
\begin{tabbing}
  \texttt{{\small \tag{n}}}\hspace{1.5em} \=  Noun\\[-0.5ex]
%  \texttt{{\small <np>}} \> Proper noun\\[-0.5ex]
  \texttt{{\small \tag{v}}} \>  Verb\\[-0.5ex]
  \texttt{{\small \tag{prn}}} \> Pronoun \\[-0.5ex]
  \texttt{{\small \tag{det}}} \>  Determiner\\[-0.5ex]
%  \texttt{{\small <cnjcoo>}} \> Coord. conjunct.\\[-0.5ex]
%  \texttt{{\small <cnjadv>}} \> Adv. conjunct.\\[-0.5ex]
  \texttt{{\small \tag{adj}}} \> Adjective\\[-0.5ex]
  \texttt{{\small \tag{adv}}} \> Adverb\\[-0.5ex]
%  \texttt{{\small <vaux>}} \> Auxiliary verb\\[-0.5ex]
%  \texttt{{\small <cop>}} \> Copula\\[-0.5ex]
  \texttt{{\small \tag{iv}}} \> Intransitive\\[-0.5ex]
  \texttt{{\small \tag{tv}}} \> Transitive\\[-0.5ex]
%  \texttt{{\small <p2>}} \> Second person\\[-0.5ex]
  \texttt{{\small \tag{p3}}} \> Third person\\[-0.5ex]
%  \texttt{{\small <ant>}} \> Anthroponym\\[-0.5ex]
%  \texttt{{\small <dem>}} \> Demonstrative\\[-0.5ex]
%  \texttt{{\small <m>}} \> Masculine\\[-0.5ex]
%  \texttt{{\small <sg>}} \> Singular\\[-0.5ex]
  \texttt{{\small \tag{pl}}} \> Plural\\[-0.5ex]
  \texttt{{\small \tag{ref}}} \> Reflexive \\[-0.5ex]
  \texttt{{\small \tag{pers}}} \> Personal \\[-0.5ex]
  \texttt{{\small \tag{nom}}} \> `Nominative'\\[-0.5ex]
  \texttt{{\small \tag{gen}}} \> Genitive\\[-0.5ex]
  \texttt{{\small \tag{acc}}} \> Accusative\\[-0.5ex]
  \texttt{{\small \tag{dat}}} \> Dative\\[-0.5ex]
  \texttt{{\small \tag{qnt}}} \> Quantifier \\[-0.5ex]
%  \texttt{{\small \tag{itg}}} \> Interrogative \\[-0.5ex]
%  \texttt{{\small <loc>}} \> Locative\\[-0.5ex]
%  \texttt{{\small <px3sg>}} \> 3rd person poss. (Singular)\\[-0.5ex]
  \texttt{{\small \tag{cm}}} \> Comma\\[-0.5ex]
  \texttt{{\small \tag{sent}}} \hspace{0.2em} \= Sentence\\[-0.5ex]
%  \texttt{{\small <px3pl>}} \> 3rd person poss. (Plural)\\[-0.5ex]
%  \texttt{{\small <neg>}} \> Negative\\[-0.5ex]
%  \texttt{{\small <aor>}} \> Aorist\\[-0.5ex]
  \texttt{{\small \tag{past}}} \> Past (General) \\[-0.5ex]
  \texttt{{\small \tag{ifi}}} \> Past \\[-0.5ex]
  	\> \hspace{0.5em}(Eyewitness/Recent) \\[-0.5ex]
%  \\[-0.5ex]
%  \\[-0.5ex]
  \texttt{{\small \tag{px3sp}}} \> 3rd person poss.\\[-0.5ex]
  	\> \hspace{0.5em}(Singular/Plural)\\[-0.5ex]
%  \texttt{{\small <imp>}} \> Imperative\\[-0.5ex]
  \texttt{{\small \tag{gna\_perf}}} \hspace{0.05em} \= Verbal adverb \\[-0.5ex]
  	\> \hspace{0.5em}(Perfect)\\[-0.5ex]
  \texttt{{\small \tag{gpr\_past}}} \> Verbal adjective \\[-0.5ex]
  	\> \hspace{0.5em}(Past)\\[-0.5ex]
  \texttt{{\small \tag{ger\_past}}} \> Verbal noun \\[-0.5ex]
	\> \hspace{0.5em} (Past)
%  \texttt{{\small <prc\_impf>}} \> Participle (Imperfect)\\[-0.5ex]
%  \texttt{{\small <prc\_irre>}} \> Participle (Irrealis)\\[-0.5ex]
%  \texttt{{\small <prc\_real>}} \> Participle (Realis)\\[-0.5ex]

@@

		\headerbox{Categorisation}{name=lexc,below=exout,column=1}{
		%\headerbox{Morphophonology}{name=morphophon,below=morphtrans}{
			\begin{itemize}
				\item Example:\ morphologically distinct adjective classes (not documented elsewhere)
				\item Other Turkic transducers:\ \texttt{0}-derivation (\hilitetwo{overgenerates})
				\item Our approach:\ categorisation (generates/analyses only correct forms)
			\end{itemize}

@@

%		\scalebox{0.8}{
%			\begin{tabular}{lll}
%				\toprule
%				\textbf{type} & \textbf{lang} & \textbf{contents} \\ % & \textbf{origin} \\
%				\midrule
%				Encyclopædic & kaz & Wikipedia \\ % wpdump & 20131006 \\
%					& tat & Wikipedia \\ % wpdump & 20130225 \\
%					& kum & — \\ % — & — \\
%				\midrule
%				News & kaz & RFE/RL (azattyq.org) \\ % RFE/RL & azattyq.org 2010 \\
%					& tat & tat.tatar-inform.ru \\ % Татар-информ & tat.tatar-inform.ru 2005-2011 \\
%					& kum & Ёлдаш (yoldash.etnosmi.ru) \\ % Ёлдаш & yoldash.etnosmi.ru \\
%				\midrule
%				Religion & kaz & Quran + Bible \\ % quran + bible & kkitap.net, kuran.kz \\
%					& tat & Quran + New Testament \\ % quran + nt & ibt.org.ru, tanzil.net \\
%					& kum & Genesis + New Testament \\ % genesis + nt & ibt.org.ru \\
%				\bottomrule
%			\end{tabular}
%		}
		\scalebox{0.77}{
			\begin{tabular}{llll}
				\toprule
					& \textbf{Wikipedia} & \textbf{News} & \textbf{Religion} \\
				\midrule
					\texttt{\textbf{kaz}} & Wikipedia & azattyk.org & Quran + Bible \\
					\texttt{\textbf{tat}} & Wikipedia & tat.tatar-inform.ru & Quran + New Testament \\
					\texttt{\textbf{kum}} & --- & yoldash.etnosmi.ru & Genesis + New Testament \\
				\bottomrule
			\end{tabular}

@@

					\multirow{3}{*}{\texttt{\textbf{tat}}} & \multirow{3}{*}{{\qipa е}} & {\qipa э / C \_} & {\qipa дәр\hiliteone{е}сл\hilitetwo{ә}р} \eng{lessons} \\
						&	& {\qipa /j/+ы} & {\qipa \hiliteone{е}лл\hilitetwo{а}р} \eng{years} \\
						&	& {\qipa /j/+э} & {\qipa \hiliteone{е}гетл\hilitetwo{ә}р} \eng{boys} \\
				\midrule

@@

				\item Turkic RBMT mailing list (>25 subscribers):\\
				\texttt{apertium-turkic@lists.sourceforge.net}\\
				\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item See our papers in LREC proceedings\\
				(2012:\ Kyrgyz, 2014:\ Kazakh, Tatar, Kumyk)
				\item And feel free to contact the authors any time!
			\end{itemize}
			%\vspace{2.8ex}
		}
